\section{Matrix completion as a predictor}

A dataset of peptide-MHC affinities for $n$ peptides and $a$ alleles may be thought of as a $n \times a$ matrix where peptide/allele pairs without measurements are missing values. The task of predicting values at these positions is known as matrix completion, and various heuristic and optimization-based algorithms have been proposed. We first investigated the performance of several matrix completion algorithms as a standalone solution to the peptide-MHC affinity prediction problem. The algorithms considered were:

\begin{itemize}
\item {\bf meanFill}: Replace each missing pMHC binding affinity with the mean affinity for that allele. This is a very simple imputation method which serves as a baseline against which other methods can be compared. 

\item {\bf knnImpute}~\cite{Troyanskaya_2001}: Each missing entry $X_{ij}$ is imputed using the values in the $k$ closest columns with observation in row $i$.  Similarity between alleles is computed as $e^{-d_{st}^2}$, where $d_{st}$ is the mean squared difference between observed entries of alleles $s$ and $t$. 

\item {\bf svdImpute}~\cite{Troyanskaya_2001}: Imputation using iterative fixed rank SVD decomposition. 

\item {\bf softImpute}~\cite{Mazumder2010SpectralMatrices}: A singular value thresholding method which iteratively estimates a low-rank matrix completion without forcing the pre-specification of a particular solution rank. Instead, the {\it softImpute} method is parameterized by a shrinkage value $\lambda$ that is subtracted from each singular value. 

\item {\bf MICE}~\cite{Azur_2011}: Average multiple imputations generated using Gibbs sampling from the joint distribution of columns. 
\end{itemize}

We evaluated the performance of these methods using five fold cross validation on BD2009 (~\ref{tab:imputation}). As MICE outperformed the other methods on two of the three predictor metrics, we selected it for the subsequent neural network experiments.

\begin{table}[htbp]
\centering
\begin{tabular}{cl||ccc}
\toprule
Imputation Method & Parameter & AUC & $F_1$ score & Kendall's $\tau$ \\
\midrule 
meanFill &   & 0.6590  & 0.0677 & 0.1836 \\
\midrule
knnImpute & $k = 1$ & 0.8088 & 0.6096 & 0.4515\\
  & $k = 3$ & 0.8202 & 0.6054 & 0.4358 \\
  & $k = 5$ & 0.8164 & 0.5884 & 0.4228 \\
\midrule
MICE & $n = 25$ & \bf{0.8675} & \bf{0.6292} & 0.4635 \\
\midrule
softImpute & $\lambda=1$ & 0.8296 & 0.5126 & \bf{0.4767} \\
& $\lambda=5$ & 0.8266 & 0.4930 & 0.4689 \\
& $\lambda=10$ & 0.7903 & 0.3835 & 0.4153 \\
\midrule
svdImpute & rank = 5 & 0.8271 & 0.6201 & 0.4313 \\
& rank = 10 & 0.8283 & 0.6201 & 0.4301 \\
& rank = 20 & 0.8272 & 0.6270 & 0.4292  \\
\bottomrule[1.25pt]
\end{tabular}
\begin{center}
\caption{Cross validation performance of several matrix completion algorithms on BD2009} \label{tab:imputation}
\end{center}
\end{table}

